IJCAI--16 Formatting Instructions\thanks{These match the formatting instructions of IJCAI-07. The support of IJCAI, Inc. is acknowledged.}

### 2016-09-30 Papers/2014/WADT/BenzmuellerWoltzenlogelPaleo/paper.tex

\bibitem{C40}
C. Benzm{\"u}ller and B.~Woltzenlogel Paleo.
\newblock Automating {G\"{o}del's} ontological proof of god's existence with
  higher-order automated theorem provers.
\newblock In 
  {\em ECAI 2014}, volume 263 of {\em Frontiers in Artificial Intelligence and
  Applications}, pages 163 -- 168. IOS Press, 2014.

@@

@@

\bibitem{CSR}
C.~Benzm{\"u}ller and B. Woltzenlogel Paleo.
\newblock Interacting with Modal Logics in the Coq Proof Assistant, {\em 10th International Computer Science Symposium in Russia (CSR)}, 2015.

>>>>

\bibitem{C40}
C. Benzm{\"u}ller and B.~Woltzenlogel Paleo.
\newblock Automating {G\"{o}del's} ontological proof of god's existence with
  higher-order automated theorem provers.
\newblock In 
  {\em ECAI 2014}, volume 263 of {\em Frontiers in AI and
  Applications}, pages 163 -- 168. IOS Press, 2014.

@@

\bibitem{CSR}
C.~Benzm{\"u}ller and B. Woltzenlogel Paleo.
\newblock Interacting with Modal Logics in the Coq Proof Assistant,
{\em 10th Intl. Computer Science Symp. in Russia (CSR)}, 2015.

@@

### 2016-09-30 Papers/2016/IJCAI/ijcai16.tex

%%%% ijcai15.tex

\typeout{IJCAI-15 Instructions for Authors}

% These are the instructions for authors for IJCAI-15.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{article}
% The file ijcai15.sty is the style file for IJCAI-15 (same as ijcai07.sty).
\usepackage{ijcai15}

% Use the postscript times font!
\usepackage{times}

@@

\title{IJCAI--15 Formatting Instructions\thanks{These match the formatting instructions of IJCAI-07. The support of IJCAI, Inc. is acknowledged.}}
\author{Qiang Yang \\
Hong Kong University of Science and Technology\\
Hong Kong, China \\
pcchair15@ijcai.org}

@@

\begin{abstract}
  The {\it IJCAI--15 Proceedings} will be printed from electronic
  manuscripts submitted by the authors. The electronic manuscript will
  also be included in the online version of the proceedings. This paper
  provides the style instructions.
\end{abstract}

@@

The {\it IJCAI--15 Proceedings} will be printed from electronic
manuscripts submitted by the authors. These must be PDF ({\em Portable
Document Format}) files formatted for 8-1/2$''$ $\times$ 11$''$ paper.

@@

The \LaTeX{} and Word style files are available on the IJCAI--15
website, {\tt http://www.ijcai-15.org/}.
These style files implement the formatting instructions in this
document.

The \LaTeX{} files are {\tt ijcai15.sty} and {\tt ijcai15.tex}, and
the Bib\TeX{} files are {\tt named.bst} and {\tt ijcai15.bib}. The
\LaTeX{} style file is for version 2e of \LaTeX{}, and the Bib\TeX{}
style file is for version 0.99c of Bib\TeX{} ({\em not} version
0.98i). The {\tt ijcai15.sty} file is the same as the {\tt
ijcai07.sty} file used for IJCAI--07.

The Microsoft Word style file consists of a single file, {\tt
ijcai15.doc}. This template is the same as the one used for
IJCAI--07.

@@

Further information on using these styles for the preparation of
papers for IJCAI--15 can be obtained by contacting {\tt
pcchair15@ijcai.org}.

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{ijcai15}

>>>>

%%%% ijcai16.tex

\typeout{IJCAI-16 Instructions for Authors}

% These are the instructions for authors for IJCAI-16.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{article}
% The file ijcai16.sty is the style file for IJCAI-16 (same as ijcai07.sty).
\usepackage{ijcai16}

% Use the postscript times font!
\usepackage{times}
%The following must be included in the document preamble (it cannot be included in a script), 
%without ANY LaTeX coding — even an accent:
\pdfinfo{
/Title ()
/Author () }
%Here's an example of properly completed pdfinfo (note that there is no accent mark in 
%Bessière, there are no LaTex codes, and the names are separated only by commas):
%\pdfinfo{
%/Title (Arc-Consistency and Arc-Consistency Again)
%/Author (Christian Bessiere, Marie-Odile Cordier) }

@@

\title{IJCAI--16 Formatting Instructions\thanks{These match the formatting instructions of IJCAI-07. The support of IJCAI, Inc. is acknowledged.}}
\author{Subbarao Kambhampati \\ 
Arizona State University, Tempe Arizona  \\
ijcai16programchair@gmail.com}

@@

\begin{abstract}
  The {\it IJCAI--16 Proceedings} will be printed from electronic
  manuscripts submitted by the authors. The electronic manuscript will
  also be included in the online version of the proceedings. This paper
  provides the style instructions.
\end{abstract}

@@

The {\it IJCAI--16 Proceedings} will be printed from electronic
manuscripts submitted by the authors. These must be PDF ({\em Portable
Document Format}) files formatted for 8-1/2$''$ $\times$ 11$''$ paper.

@@

The \LaTeX{} and Word style files are available on the IJCAI--16
website, {\tt http://www.ijcai-16.org/}.
These style files implement the formatting instructions in this
document.

The \LaTeX{} files are {\tt ijcai16.sty} and {\tt ijcai16.tex}, and
the Bib\TeX{} files are {\tt named.bst} and {\tt ijcai16.bib}. The
\LaTeX{} style file is for version 2e of \LaTeX{}, and the Bib\TeX{}
style file is for version 0.99c of Bib\TeX{} ({\em not} version
0.98i). The {\tt ijcai16.sty} file is the same as the {\tt
ijcai07.sty} file used for IJCAI--07.

The Microsoft Word style file consists of a single file, {\tt
ijcai16.doc}. This template is the same as the one used for
IJCAI--07.

@@

Further information on using these styles for the preparation of
papers for IJCAI--16 can be obtained by contacting {\tt
ijcai16programchair@gmail.com}.

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{ijcai16}
